---
title: "Report"
author: "Hadi Sam Nariman"
date: "January 13, 2018"
output: html_document
---

Uploading Needed Packages 
```{r setup, message = FALSE}
library(ggraph)
library(qgraph)
library(lavaan)
library(broom)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(semPlot)
library(haven)
library(psych)
library(MVN)
library(stargazer)
library(car)
library(dplyr)
library(tibble)
```

Reading the Dataset 

```{r message = FALSE}

coll_df = read.table("C:\\Users\\User\\Desktop\\To Mac\\Hadi-Final-Project\\Dataframe.dat", header=TRUE)
View (coll_df)
```

##Exploratory Data Analyses
Exploring Missing Variables in the Dataset

```{r}
sapply(coll_df,function(x) sum(is.na(x)))
```

Exploring the Nature of the Variables 

```{r}
summary(coll_df)
```

###Check for outliers
Boxplots 

```{r}
attach(coll_df)
coll_df %>% 
  gather(variable, value) %>%
  ggplot() + 
  aes(x = fct_rev(variable), y = value) +
  geom_boxplot() +
  coord_flip()
detach(coll_df)
```

Inquring into q6_6 with an outlier

```{r}
outlierKD <- function(dt, var) {
     var_name <- eval(substitute(var),eval(dt))
     na1 <- sum(is.na(var_name))
     m1 <- mean(var_name, na.rm = T)
     par(mfrow=c(2, 2), oma=c(0,0,3,0))
     boxplot(var_name, main="With outliers")
     hist(var_name, main="With outliers", xlab=NA, ylab=NA)
     outlier <- boxplot.stats(var_name)$out
     mo <- mean(outlier)
     var_name <- ifelse(var_name %in% outlier, NA, var_name)
     boxplot(var_name, main="Without outliers")
     hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
     title("Outlier Check", outer=TRUE)
     na2 <- sum(is.na(var_name))
     cat("Outliers identified:", na2 - na1, "n")
     cat("Propotion (%) of outliers:", round((na2 - na1) / sum(!is.na(var_name))*100, 1), "n")
     cat("Mean of the outliers:", round(mo, 2), "n")
     m2 <- mean(var_name, na.rm = T)
     cat("Mean without removing outliers:", round(m1, 2), "n")
     cat("Mean if we remove outliers:", round(m2, 2), "n")
     response <- readline(prompt="Do you want to remove outliers and to replace with NA? [yes/no]: ")
     if(response == "y" | response == "yes"){
          dt[as.character(substitute(var))] <- invisible(var_name)
          assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
          cat("Outliers successfully removed", "n")
          return(invisible(dt))
     } else{
          cat("Nothing changed", "n")
          return(invisible(var_name)) }}
outlierKD(coll_df, q6_9)
```

###Tests of Normality

```{r}
coll_df %>% 
  gather(variable, value) %>%
  ggplot() + 
  aes(x = value) +
  geom_freqpoly() +
  facet_wrap(~variable)
```

###Correlation Analyses
####Correlation Between Sets of Items Representing the Dependent Latent Variables Analysed in the SEM Models Later

Correlation between Items represnting Political Support and the Plot

q18_1. Muslims are allowed to politically organize themselves in the Netherlands in order to try to influence policy.
q18_4. Muslims are allowed to exercise important official duties (mayor, minister) in the Netherlands.

```{r}
cor(coll_df$q18_1 , coll_df$q18_4)
ggplot(coll_df) +
  aes(x = q18_1 , y = q18_4) +
  geom_point(position = "jitter") + 
  geom_smooth(method="lm")
```

Correlation between Items represnting Realistic Support and the Plot

q18_3. Muslims are allowed to maintain their cultural identity.
q18_6. Muslims are entitled to their own culture and traditions.

```{r}
cor(coll_df$q18_3 , coll_df$q18_6)
ggplot(coll_df) +
  aes(x = q18_3 , y = q18_6) +
  geom_point(position = "jitter") + 
  geom_smooth(method="lm")
```

Correlation between Items represnting Cultural Support and the Plot

q18_2. Much more attention is needed for discrimination of Muslims on the labour market.
q18_5. Better care should be taken of ensuring Muslims equal opportunities to get a good job.

```{r}
cor(coll_df$q18_2 , coll_df$q18_5)
ggplot(coll_df) +
  aes(x = q18_2 , y = q18_5) +
  geom_point(position = "jitter") + 
  geom_smooth(method="lm")
```

####Correlation between Three Froms of Threat (Symbolic, Realistic, and Collective Ownership) in a Path Analysis 

```{r}
model <- ' st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
ct =~ q16_9 + q16_10 + q16_11 + q16_12
st ~~ rt
st ~~ ct
rt ~~ ct'
cormodel <- sem(model, data=coll_df)
summary(cormodel, fit.measures=TRUE, standardized=TRUE)
semPaths(cormodel, "Standardized", "Estimates")
```

#Hypothesis I
##Structural Equation Modeling 
### Confirmatory Factor Analyses

Confirmatory factor analyses were computed for all latent variables (both independent and dependent). Regarding the dependent constructs, the model $x^{2}$ of 12.131 showed a marginal absolute fit (*p* = .0591), while other measures confirmed that the model fit is satisfactory: CFI = .995; TLI = .989; SRMR = .012; and RMSEA = .048 and 90% CI = .001 - .088. All the factor loadings were statistically significant (*p* < .001) and the standardized factor loadings were between .78 and .92. 
The model $x^{2}$ of 60.625 of the independent variables indicated a good model fit too (*p* = .1044) which was confirmed by other measures of model fit: CFI = .998; TLI = .998; SRMR = .01; and RMSEA = .02 and 90% CI = 0.001 - 0.042. All the factor loadings were statistically significant (*p* < .001) and the standardized factor loadings were between .83 and .95. Moreover, in order to improve the model fit, errors of two items from the symbolic threat scale and three items from the realistic threat scale were allowed to covary.

####Conformatory Factor Analysis of the Dependent Variables 
Model Specification 

```{r}
modeldv <- ' pol =~ q18_1 + q18_4
real =~ q18_3 + q18_6
cul =~ q18_2 + q18_5'
fitdv <- cfa(modeldv, data=coll_df, std.lv=TRUE,missing="fiml")
```

Model Results and Plot 

```{r}
summary(fitdv, fit.measures=TRUE, standardized=TRUE)
semPaths(fitdv, "Standardized", "Estimates")
```

####Conformatory Factor Analysis of the Independent Variables
Model Specification

```{r}
modeliv <- ' st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
co =~ q16_9 + q16_10 + q16_11 + q16_12'

fitiv <- cfa(modeliv, data=coll_df, std.lv=TRUE,missing="fiml")
```

Model Results 

```{r}
summary(fitiv, fit.measures=TRUE, standardized=TRUE)
```

Model Modification 

```{r}
modificationIndices(fitiv, sort.=TRUE, minimum.value=3)
```

Modified Model

```{r}
modeliv <- 'sT =~ q16_1 + q16_2 + q16_3 + q16_4
rT =~ q16_5 + q16_6 + q16_7 + q16_8
cO =~ q16_9 + q16_10 + q16_11 + q16_12
q16_4 ~~ q16_1
q16_7 ~~ q16_5
q16_8 ~~ q16_5'
fitiv <- cfa(modeliv, data=coll_df, std.lv=TRUE,missing="fiml")
```

Model Results and Plot

```{r}
summary(fitiv, fit.measures=TRUE, standardized=TRUE)
semPaths(fitiv, "Standardized", "Estimates")
```

###Structural Model 
The structural model indicated a good model fit ($x^{2} = 139.358$ ; df = 117; CFI = .997; TLI = .997; RMSEA = .021 with 90% CI = .001- .033). Hence, the model fit manifests that the model is apt to explaining the association among the constructs. The path coefficients from symbolic threat to political ($\beta$ = -.36, *p* = .023), cultural ($\beta$ = -.385, *p* = .031), and real support ($\beta$ = -.438, *p* = .009) were significantly negative. The path coefficients from realistic threat to political ($\beta$ = -.259, *p* = .02), cultural ($\beta$ = -0.28, *p* = .02), and real support ($\beta$ = -.327, *p* = 0.005) were also significantly negative. Path coefficient of collective ownership threat to the three forms of support, however, were not found significant. Hence, the higher perception of realistic and symbolic types of threat the lesser tendency on the support for integration of Muslims in the Netherlands.

```{r}
model <- 'pol =~ q18_1 + q18_4
real =~ q18_3 + q18_6
cul =~ q18_2 + q18_5
st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
co =~ q16_9 + q16_10 + q16_11 + q16_12
pol ~ st + rt + co
real ~ st + rt + co
cul ~ st + rt + co
pol ~~ real
pol ~~ cul
real ~~ cul'
fitsem <- cfa(model, data=coll_df, std.lv=TRUE,missing="fiml")
summary(fitsem, fit.measures=TRUE)
```

Mdel Modification 

```{r}
modificationIndices(fitsem, sort.=TRUE, minimum.value=3)
```

Modified Model Fit of the Structural Model 

```{r}
model<- 'pol =~ q18_1 + q18_4
real =~ q18_3 + q18_6
cul =~ q18_2 + q18_5
st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
co =~ q16_9 + q16_10 + q16_11 + q16_12
pol ~ st + rt + co
real ~ st + rt + co
cul ~ st + rt + co
q16_7 ~~ q16_5   
q16_8 ~~ q16_5
q16_4 ~~ q16_1
pol ~~ real
pol ~~ cul
real ~~ cul'
fitsem <- cfa(model, data=coll_df, std.lv=TRUE,missing="fiml")
summary(fitsem, fit.measures=TRUE)
```

Modified Strucrural Model results and Plot 

```{r}
model<- 'pol =~ q18_1 + q18_4
real =~ q18_3 + q18_6
cul =~ q18_2 + q18_5
st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
co =~ q16_9 + q16_10 + q16_11 + q16_12
pol ~ st + rt + co
real ~ st + rt + co
cul ~ st + rt + co
q16_7 ~~ q16_5   
q16_8 ~~ q16_5
q16_4 ~~ q16_1
pol ~~ real
pol ~~ cul
real ~~ cul'
smodel <- sem(model, data=coll_df)
summary(smodel, standardized=TRUE)
semPaths(smodel, "Standardized", "Estimates")
```

#Hypothesis II
##Structural Equation Modeling 
A structural equation modeling was conducted to measure the effect of three forms of threat on thermometer questions. The chi-square test didn't show an absolute fit ($x^{2} = 185.963$; df = 84; *p* < .001). However, other measures indicated a satisfactory model fit in general; CFI = .987; TLI = .984; SRMR = .023; and RMSEA = .053 and 90% CI < 0.043 - .063. The results showed that the path coefficients from symbolic threat to thermometer questions ($\beta$ = -.446, *p* = .003) were found to be significant. In other words, the higher the symbolic threat the more negative feelings are perceived. No significant statistics were found from the path coefficients of collective ownership and realistic types of threat on the thermometer questions.

Model Fit 

```{r}
model<- 'thermo =~ q6_6 + q6_9 + q6_10
st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
co =~ q16_9 + q16_10 + q16_11 + q16_12
thermo ~ st + rt + co'
fitsem <- cfa(model, data=coll_df, std.lv=TRUE,missing="fiml")
summary(fitsem, fit.measures=TRUE)
```

Model Specification,Results, and Plot 

```{r}
model<- 'thermo =~ q6_6 + q6_9 + q6_10
st =~ q16_1 + q16_2 + q16_3 + q16_4
rt =~ q16_5 + q16_6 + q16_7 + q16_8
co =~ q16_9 + q16_10 + q16_11 + q16_12
thermo ~ st + rt + co'
Thermomodel <- sem(model, data=coll_df)
summary(Thermomodel, standardized=TRUE)
semPaths(Thermomodel, "Standardized", "Estimates")
``````